---
output:
  md_document:
    variant: markdown_github
---

# Purpose



```{r}

rm(list = ls()) # Clean your environment:
gc() # garbage collection - It can be useful to call gc after a large object has been removed, as this may prompt R to return memory to the operating system.
library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

> Packages  The following code is utilised to first load relevant packages that is most appropriate for this project.The location of the project is also added. 

```{r}
library(Texevier)
library(fmxdat)
library(dplyr)
library(tidyverse)
library(readxl)
library(lubridate)

location <- "C:/Users/tashe/Desktop/20772998"
```
A folder for each question will be created and formatted according to the Practical test requirements.

# Question One 
> A Texevier (PDF and HTML) folder is required for this quesiton. 

```{r}
Texevier::create_template(directory = glue::glue("{location}/"), template_name = "Question 1" )
```


# Question 2
> A Texevier (PDF and HTML) folder is required for this quesiton. 

```{r}
Texevier::create_template(directory = glue::glue("{location}/"), template_name = "Question 2")
```

# Question 3
> Need to create a folder, utilising teh fmxdat function. 

```{r}
fmxdat::make_project()
```


# Question 4
> A Texevier (PDF and HTML) folder is required for this quesiton.

```{r}
Texevier::create_template(directory = glue::glue("{location}/"), template_name = "Question 4")
```

