---
output:
  md_document:
    variant: markdown_github
---

# Practical 
The following practical is set-up in the following manner. Each question's answers can be found each folder's rmd or pdf; each dependent on what format the question requires.

> Packages  The following code is utilised to first load relevant packages that is most appropriate for this project.The location of the project is also added. 

```{r }
# library(Texevier)
# library(fmxdat)
# library(dplyr)
# library(tidyverse)
# library(readxl)
# library(lubridate)

location <- "C:/Users/tashe/Desktop/20772998"
```
A folder for each question will be created and formatted according to the Practical test requirements. The code appropriate for each quesiton can be found in the _code_ folder in each question. The relevant data sets can be found in the _data_ folder.

# Question One 
> A Texevier (PDF and HTML) folder is required for this quesiton. 

```{r}
Texevier::create_template(directory = glue::glue("{location}/"), template_name = "Question 1" )
```
I unfortunately did not manage to complete this question. The code found in the code folder was my attempt at this question. The large data set caught me off-guard, and I wasted a day going in a circle. 

# Question 2
> A Texevier (PDF and HTML) folder is required for this quesiton. 

```{r}
Texevier::create_template(directory = glue::glue("{location}/"), template_name = "Question 2")
```
Question two is my attempt at trying to get a colleague to stay in Cape Town. Please do read the PDF in the Question 2 folder. The code for the graphs and tables can be found in the _code_ folder.

# Question 3
> Need to create a folder, utilising teh fmxdat function. 

```{r}
fmxdat::make_project()
```
A normal project folder was created for this question. The Rmd file can be used to view my attempt at comring the two bands.

# Question 4
> A Texevier (PDF and HTML) folder is required for this quesiton.

```{r}
Texevier::create_template(directory = glue::glue("{location}/"), template_name = "Question 4")
```
The final answers to this question can be found in the PDF document in the folder, Question 4. 

# Question 5
> A Texevier (PDF and HTML) folder is required for this quesiton.

```{r}
Texevier::create_template(directory = glue::glue("{location}/"), template_name = "Question 5")
```
I did not manage to convert this document into a PDF. Thus, the rmd is my attempt for this question and the appropriate code is in the _code_ folder in the Question 5 folder.


