---
title: "London is looking a bit Grey"
documentclass: elsarticle
Thesis_FP: no
output:
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
  html_document:
    df_print: paged
Author1: Tashen Naidoo
Ref1: MCom Economics Student, Stellenbosch University, South Africa
Email1: 20772998\@sun.ac.za
CorrespAuthor_1: yes
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: "Let it be known that Cape Town is better than London, at least  in terms
  of the weather. The following statistical finds will make that clear. \n"
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(Texevier)
library(fmxdat)
library(dplyr)
library(readxl)
list.files('Question2/code/', full.names = T, recursive = T) %>% as.list()

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}
London may be a first world country, but there is a reason why they drink so much tea - it's all due to the weather. I have utilised the UK National Weather Service data set to compare if London is all sunshine, as you believe. I will be making comparisons between Cape Town and London's weather. 

> If this does not convince you to stay, don't forget your umbrella! 


# Data  {-}
The UK National Weather Service data set was used and this website [love Cape Town](https://www.capetown.travel/plan-your-trip/weather-in-cape-town/) to get the average temparatures in the Mother City. 

Let's first take a look at Londons Weather over time. 



```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "London's Average Weather Over Time \\label{Figure1}", fig.ext = 'png', fig.height = 6, fig.width = 6}
source("code/avg_plot.R")
source("code/clean_data.R")
ot <- over_time(london_weather)
ot
```

This figure shows that London spends most of its time under the shadow of clouds. To make it clearer, take a look at the following weather type comparisons.

```{r Figure2, warning =  FALSE, fig.align = 'center', fig.cap = "Average Weather Conditions \\label{Figure2}", fig.height = 5, fig.width = 6, dev = 'png'}


source("code/tbl_avg.R") 
av <- overall_mean(london_weather)
av

```

Now it is much clearer that over several decades, London has spent nearly 47 percent under cloud cover and under 40 percent enjoying the sunshine. ALotugh you may not need to take an umbrella, as the chances of rain/precipitation is low, I don't think you need as much sunblock as what you think you need. 

# Seasons
Now let's take a look at the average maximum and minimum temperature that you can expect during every season in London. 
```{r Figure3, warning =  FALSE, fig.align = 'center', fig.cap = "Average Season Temperature \\label{Figure3}", fig.height = 4, fig.width = 5, dev = 'png'}

source("code/bar_plot.R")
b <- seasonal(london_weather)
b
```


The average maximum temperature in London is 22.67 degrees Celsius. My word! This explains why everyone in London flocks to the beach when they have "good weather" in the Summer. 

The average temperatures can be enjoyed in Cape Town:  
+ Summer: 20-30 degrees Celsius  
+ Spring and Autumn: mid teens to mid 20's  
+ Winter: mid teens to low 20's 

# Conclusion
If this doesn't convince you stay in Cape Town, then I don't know what else will. You want to go based on your belief that it is sunnier, but I hope this has shed some more light to what you can expect. 

> If you do go, at least enjoy the English Premier League


<!-- Make title of bibliography here: -->
<!-- \newpage -->





